The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-13 document/ms.tex
masstab

>>>>

\section{Comparison with the literature}\sectlabel{comparison}

\begin{floattable}
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\caption{The inferred parameters for the long-period transiting exoplanet
candidates \label{tab:masses}}
\include{masstab}
\tablenotetext{*}{The equilibrium temperature is computed assuming zero
albedo.}
\end{deluxetable}
\end{floattable}

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=\textwidth]{figures/completeness-am.pdf}
\end{center}
\caption{%
The same as \dfmfig{completeness} converted into the planet mass and
semi-major axis plane.
Since the completeness function depends on the planet's radius and not its
mass, a probabilistic mass--radius relation \citep{Chen:2016} was used to
convert radius to mass.
\dfmfiglabel{completeness-am}}
\end{figure*}
